---
title       : Normal Distribution Calculator
subtitle    : A Handy Shiny App Calculating Normal Distribution
author      : QIU Hongxiang
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides


--- &radio

## Introduction to Normal Distribution and App

* Normal distribution: widely used; hard to calculate by hand or simple calculators. Weird probability density function with no elementary anti derivative:$f(x)=\frac{1}{\sigma \sqrt{2\pi}} e^{-\frac{(x-\mu)^2}{2\sigma^2}}$
* Three common values to calculate given parameters of a normal distribution: cumulative probability, density and quantile.
* This Shiny App can do all these calculations without knowledge in programming.
* What else can you do with this App?

1. Generate random numbers
2. _Plot_
3. Calculte t distribution
4. Nothing

*** .hint

Go to http://davidqiu.shinyapps.io/CourseraDevelopingDataProductsShiny and check out!

---

## Function 1: Probability

* Select "Probability" in "Kind of Parameter" and input parameters to determine normal distribution.
* Input Known and click "Claculate!" button to calculate P(x<Known).
* What's running behind?
    + The App runs `pnorm(Known, Mean, Standard Deviation)` function in R.
    + For example,Known=15,  Mean=10, Standard Deviation=5, the result is:
    ```{r}
    pnorm(15,10,5)
    ```


---

## Function 2: Density

* Select "Density" in "Kind of Parameter" and input parameters to determine normal distribution.
* Input Known and click "Claculate!" button to calculate f(Known).
* What's running behind?
    + The App runs `dnorm(Known, Mean, Standard Deviation)` function in R.
    + For example,Known=15,  Mean=10, Standard Deviation=5, the result is:
    ```{r}
    dnorm(15,10,5)
    ```


---

## Function 3: Quantile

* Select "Quantile" in "Kind of Parameter" and input parameters to determine normal distribution.
* Input Known and click "Claculate!" button to calculate X such that P(x<X)=Known.
* What's running behind?
    + The App runs `qnorm(Known, Mean, Standard Deviation)` function in R.
    + For example,Known=0.6, Mean=10, Standard Deviation=5, the result is:
    ```{r}
    qnorm(.6,10,5)
    ```
